Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-08 appendix.tex
svgtex

>>>>

(2) \ul{Embedding Space Assumption.}

In this paper, we follow the common assumptions of deep metric
learning~\cite{revisiting} on the embedding space.
%
Namely, we assume the embedding vectors are normalized onto the real unit
hypersphere.
%
Meanwhile, the distance function $d(\cdot,\cdot)$ is assumed to be Euclidean
distance.
%
Our formulations are developed on the two assumptions.
%
It is unknown whether the proposed method method will be effective on an
embedding vectors that are NOT normalized.
%
And it is unknown whether the proposed method will be effective when
$d(\cdot,\cdot)$ is replaced as, \eg, cosine distance.
%
The gradient directions in Fig.~5 (a) in the manuscript are established on the
two assumptions (the gradient directions will differ if the two assumptions are
not satisfied).
%
We follow the common choice~\cite{revisiting,robrank} in the two aspects.
%
But we acknowledge the effectiveness of our method is unknown when the
two assumptions are broken.
%
And they may become limintations of our method.
